Efficient Handling of String-Number Conversion

### 2020-03-30 final-version/main.tex

\begin{acks}
This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no. 106-2221-E-001 -009 -MY3), Ministry of Education, Youth and Sports of Czech Republic (no. LL1908).
\end{acks}

>>>>

\begin{acks}
This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no. 106-2221-E-001 -009 -MY3), and Ministry of Education, Youth and Sports of Czech Republic (no. LL1908).
\end{acks}
